Improved Prediction of Hospital Length of Stay for Severe Injury

### 2014-09-26 poster/myposter.tex
Updated poster template to the latest style #14

\documentclass[portrait]{usydposter}
\usepackage{LI}
\usepackage{xspace}

@@

\title{CCG Parsing with One Structure per n-gram}
\author{Tim Dawborn}

\begin{document}
\makeheader

@@

% =============================================================================
\section{Heading RGB 206, 17, 38 -- Arial 28}
\noindent This is some text here...

@@

% =============================================================================
\section{Background}
\begin{itemize}
  \item \cky is a $O(n^3)$ parsing algorithm which uses a chart data structure, illustrated in Figure~1. A chart is a hierarchical triangular structure  which stores the parse trees for all substrings of the sentence being parsed
\end{itemize}

\begin{figure}
  \pgfimage[width=0.7\columnwidth]{images/chart}
  \caption{An illustration of the chart data structure used in parsing algorithms such as \cky}
\end{figure}

\begin{itemize}
  \item Combinatory Categorial Grammar (\ccg) \cite{steedman:00} is a \emph{lexicalised grammar formalism}
  \item Each word in a sentence is assigned a composite object that reflects its role within the sentence
  \item The following is an example derivation using \ccg, where the lexical categories for each token are shown
\end{itemize}

\begin{center}
  \small
  \deriv{4}{
    \rm I & \rm like & \rm the & \rm cat \\
    \uline{1} & \uline{1} & \uline{1} & \uline{1} \\
    \mc{1}{\cf{NP}} & \mc{1}{\cf{(S[dcl]\bs NP)/NP}} & \mc{1}{\cf{NP[nb]/N}} & \mc{1}{\cf{N}} \\
    & & \fapply{2} \\
    & & \mc{2}{\cf{NP[nb]}} \\
    & \bapply{3}\\
    & \mc{3}{\cf{S[dcl]\bs NP}}\\
    \bapply{4}\\
    \mc{4}{\cf{S[dcl]}}\\
  }
\end{center}

% =============================================================================
\section{Problems with Pizza}
\emph{Syntactic ambiguity} is a problem when parsing, and is a particular problem for our one structure per \ngram problem. Consider the sentence

\begin{center}
  \small
  \deriv{5}{
    \rm I & \rm ate & \rm pizza & \rm with & \rm anchovies \\
    \uline{1} & \uline{1} & \uline{1} & \uline{1} & \uline{1} \\
    \mc{1}{\cf{NP}} & \mc{1}{\cf{(S\bs NP)/NP}} & \mc{1}{\cf{NP}} & \mc{1}{\cf{(NP\bs NP)/NP}} & \mc{1}{\cf{NP}} \\
    & & & \fapply{2} \\
    & & & \mc{2}{\cf{NP\bs NP}} \\
    & & \bapply{3}\\
    & & \mc{3}{\cf{NP}}\\
    & \fapply{4} \\
    & \mc{4}{\cf{S\bs NP}} \\
    \bapply{5}\\
    \mc{5}{\cf{S}}\\
  }
\end{center}

and compare it to the sentence

\begin{center}
  \small
  \deriv{5}{
    \rm I & \rm ate & \rm pizza & \rm with & \rm cutlery \\
    \uline{1} & \uline{1} & \uline{1} & \uline{1} & \uline{1} \\
    \mc{1}{\cf{NP}} & \mc{1}{\cf{(S\bs NP)/NP}} & \mc{1}{\cf{NP}} & \mc{1}{\cf{((S\bs NP)\bs(S\bs NP))/NP}} & \mc{1}{\cf{NP}} \\
    & \fapply{2} & \fapply{2} \\
    & \mc{2}{\cf{S\bs NP}} & \mc{2}{\cf{(S\bs NP)\bs(S\bs NP)}} \\
    & \bapply{4} \\
    & \mc{4}{\cf{S\bs NP}} \\
    \bapply{5}\\
    \mc{5}{\cf{S}}\\
  }
\end{center}

These two sentences differ by only one word, yet they have two completely different derivations due to the different roles the word \textrm{with} plays in each sentence.

The word \textrm{with} thus is syntactically ambiguous. Without knowing the surrounding context, it is unknown which grammatical role the word is undertaking.

@@

\begin{center}
  \small
  \deriv{3}{
    \rm of & \rm the & \rm potato \\
    \uline{1} & \uline{1} & \uline{1} \\
    \mc{1}{\cf{(NP\bs NP)/NP}} & \mc{1}{\cf{NP/N}} & \mc{1}{\cf{N}} \\
    & \fapply{2}\\
    & \mc{2}{\cf{NP}} \\
    \fapply{3}\\
    \mc{3}{\cf{NP\bs NP}}\\
  }
\end{center}

@@

\begin{center}
  \small
  \deriv{2}{
    \rm of & \rm the \\
    \uline{1} & \uline{1} \\
    \mc{1}{\cf{(NP\bs NP)/NP}} & \mc{1}{\cf{NP/N}} \\
    \fcomp{2} \\
    \mc{2}{\cf{(NP\bs NP)/N}} \\
  }
\end{center}

@@

\begin{center}
  \small
  \deriv{3}{
    \rm of & \rm the & \rm potato \\
    \uline{1} & \uline{1} & \uline{1} \\
    \mc{1}{\cf{(NP\bs NP)/NP}} & \mc{1}{\cf{NP/N}} & \mc{1}{\cf{N}} \\
    \fcomp{2} & \\
    \mc{2}{\cf{(NP\bs NP)/N}} & \\
    \fapply{3}\\
    \mc{3}{\cf{NP\bs NP}}\\
  }
\end{center}

@@

\begin{center}
  \small
  \deriv{6}{
    \rm X & \rm on & \rm the & \rm king & \rm of & \rm England \\
    \uline{1} & \uline{1} & \uline{2} & \uline{2}  \\
    \mc{1}{\cf{NP}} & \mc{1}{\cf{(NP\bs NP)/NP}} & \mc{2}{\cf{NP[nb]}} & \mc{2}{\cf{NP\bs NP}} \\
    & & \bapply{4}\\
    & & \mc{4}{\cf{NP}}\\
    & \fapply{5} \\
    & \mc{5}{\cf{NP\bs NP}} \\
    \bapply{6} \\
    \mc{6}{\cf{NP}} \\
  }
\end{center}

@@

\begin{center}
  \small
  \deriv{6}{
    \rm X & \rm on & \rm the & \rm king & \rm of & \rm England \\
    \uline{1} & \uline{2} & \uline{1} & \uline{2}  \\
    \mc{1}{\cf{NP}} & \mc{2}{\cf{(NP\bs NP)/N}} & \mc{1}{\cf{N}} & \mc{2}{\cf{NP\bs NP}} \\
    & \fapply{3} & & \\
    & \mc{3}{\cf{NP\bs NP}} & & \\
    \bapply{4} & & \\
    \mc{4}{\cf{NP}} & & \\
    \bapply{6} \\
    \mc{6}{\cf{NP}} \\
  }
\end{center}

% =============================================================================
\section{Implementation}
The \candc parser \cite{clark-curran:07} is a state of the art \ccg parser which uses \cky. The \candc parser was used to memoise constituent-forming \ngrams into databases (Figure~2). When parsing sentences in the future, the memoised databases can be used to insert pre-constructed parses straight into the chart (Figure~3).

\begin{figure}
  \pgfimage[width=0.5\columnwidth]{images/prebuilt1}
  \caption{When creating the trigram database, a trigram is added to the database if it forms a constituent in the chart}
  \label{fig:prebuilt1}
\end{figure}

\begin{figure}
  \pgfimage[width=0.7\columnwidth]{images/prebuilt2}
  \caption{Illustration of using the \ngram databases. The trigram {\tt B~C~D} is loaded from the pre-constructed database, and blocks the corresponding cells}
\end{figure}

@@

\begin{table}
  \small
  \begin{tabular}{cc||c|cc}
    \hline
    Model & & Baseline & 2-gram & 3-gram \\
    \hline \hline
           &  Time  & 82.82   & 82.83   & 82.57  \\
    \wsj   &   LF   & 85.26   & 85.26   & 85.26  \\
    derivs &   UF   & 92.01   & 92.01   & 92.01  \\
           &   Cov  & 98.64   & 98.64   & 98.64  \\
%%%    \hline
%%%           &  Time  & 84.15   & 83.83   & 83.87  \\
%%%    \wsj   &   LF   & 87.40   & 87.40   & 87.40  \\
%%%    hybrid &   UF   & 93.10   & 93.10   & 93.10  \\
%%%           &   Cov  & 98.64   & 98.64   & 98.64  \\
%%%    \hline
%%%           &  Time  & 84.10   & 83.96   & 84.26  \\
%%%    \np    &   LF   & 83.60   & 83.60   & 83.60  \\
%%%    derivs &   UF   & 90.48   & 90.48   & 90.48  \\
%%%           &   Cov  & 98.54   & 98.54   & 98.54  \\
%%%    \hline
%%%           &  Time  & 84.82   & 84.88   & 85.32  \\
%%%    \np    &   LF   & 85.88   & 85.88   & 85.88  \\
%%%    hybrid &   UF   & 91.63   & 91.63   & 91.63  \\
%%%           &   Cov  & 98.54   & 98.54   & 98.54  \\
    \hline
  \end{tabular}
  \caption{The speed versus performance trade-off for varying sized \ngrams on \ccgbank 02 to 21}
  \label{tab:results}
\end{table}

%%%Experiments were also conducted using only non-constituent-forming \ngrams over the same datasets. However the outcome of these experiments were the same; no statistically significant change was observed.

@@

% =============================================================================
\references
\bibliography{references}

>>>>

\documentclass[landscape]{usydposter}
\usepackage{xspace}

@@

\title{Improved Prediction of Hospital Length of Stay for Severe Injury}
\author{Tianyu Pu \texttt{tianyu.pu@sydney.edu.au}}

\begin{document}

\makeheader

@@

% =============================================================================
\section{Heading RGB 0, 152, 219 -- Arial 28}
\subsection{Subheading black -- Arial 24}
\noindent This is some text here...

@@

% =============================================================================
\section{Background}

% =============================================================================
\section{Problems with Pizza}

@@

@@

@@

@@

@@

% =============================================================================
\section{Implementation}

@@

@@

% =============================================================================
\references
\bibliography{../thesis/references}
